An efficient contact value approach for the pair distribution function of the inhomogeneous hard-sphere fluid

### 2014-06-28 papers/pair-correlation/paper.tex
Only use new short range CVA in plots and walls. All plots only show fitted range. Added labels to fit plot. Tested on paho-arch. Took 0:36.79.

@@

\fixme{
  TO DO:
  \begin{itemize}
  \item \pahosays{Only use short-range CVA-S (in plots, and in walls.cpp)}
  \item \pahosays{Remove CVA from all plots, but leave it easy to
    re-add (so we can check what we say in the text).}
  \item \pahosays{Make all plots not show CVA (new name for CVA-short)
    outside the fitted range.}
  \item \davidsays{Rewrite CVA-S section to reflect new fit.}
  \item \jeffsays{Make certain when proof-reading that other prior
    formulations cannot work in ``separable'' way.}
  \item \davidsays{Be sure that we explain the fitted data and fitting
    process well.}
  \item \pahosays{Add $\eta=?$ labels and legends to new fit plot.}
  \item \jeffsays{I will diligently read what you guys write!}
  \end{itemize}
}

@@

>>>>

\usepackage{dcolumn}
\newcolumntype{d}[1]{D{.}{.}{#1}}

@@

\fixme{
  TO DO:
  \begin{itemize}
  \item \pahosays{Only use short-range CVA-S (in plots, and in walls.cpp)}\pahosays{DONE}
  \item \pahosays{Remove CVA from all plots, but leave it easy to
    re-add (so we can check what we say in the text).}\pahosays{DONE}
  \item \pahosays{Make all plots not show CVA (new name for CVA-short)
    outside the fitted range.}\pahosays{DONE}
  \item \davidsays{Rewrite CVA-S section to reflect new fit.}
  \item \jeffsays{Make certain when proof-reading that other prior
    formulations cannot work in ``separable'' way.}
  \item \davidsays{Be sure that we explain the fitted data and fitting
    process well.}
  \item \pahosays{Add $\eta=?$ labels and legends to new fit plot.}\pahosays{DONE}
  \item \jeffsays{I will diligently read what you guys write!}
  \end{itemize}
}

@@

The fit is displayed in Fig.~\ref{fig:radial-distribution}.  This
function is fit to data for $r <= \maxrfit R$.  The maximum error
within this radius in $g_S(r)$ at packing fractions up to 0.4 is
\maxerr, which occurs at $\eta = \etamaxerr$ and $r = \rmaxerr R$.
